Multivariate normal example

### 2020-05-06 src/s_ar1.Rmd
updated ar1 figures

Calculate R* and Rhat across 1000 replicates
```{r}
f_replicate <- function(){
  temp <- f_generate_lower_var_four(1/3, 0.3, 1, 1000)
  a_array <- array(dim=c(1000, 4, 1))
  a_array[,,1] <- temp
  a_accuracy <- r_star(a_array)
  mon <- monitor(temp)
  return(list(r_star=a_accuracy, r_hat=mon$Rhat))
}

@@

Look at predictions of model
```{r}
# add in a column of noise since gbm requires >1 variables
full_data <- f_generate_lower_var_four(1/3, 0.3, 1, 1000) %>% 
  melt() %>% 
  select(-Var1) %>% 
  rename(chain=Var2) %>% 
  mutate(ran_val=rnorm(4000)) %>% 
  mutate(chain=as.factor(chain))

@@

Generate R* distribution based on 1000 iterations for run where chain has lower variance and another where all four chains have same variance
```{r}
temp <- f_generate_lower_var_four(1/3, 0.3, 1, 1000) 
temp1 <- matrix(rnorm(4000), nrow = 1000)
a_array <- array(dim=c(1000, 4, 2))
a_array[,,1] <- temp
a_array[,,2] <- temp1
unmixed <- r_star_dist(a_array)

temp <- f_generate_lower_var_four(1, 0.3, 1, 1000)
temp1 <- matrix(rnorm(4000), nrow = 1000)
a_array <- array(dim=c(1000, 4, 2))
a_array[,,1] <- temp
a_array[,,2] <- temp1
mixed <- r_star_dist(a_array)

@@

>>>>

Calculate R* and Rhat across 1000 replicates
```{r}
f_replicate <- function(){
  temp <- f_generate_lower_var_four(1/3, 0.3, 1, 2000)
  a_array <- array(dim=c(2000, 4, 1))
  a_array[,,1] <- temp
  a_accuracy <- r_star(a_array)
  mon <- monitor_extra(split_data(a_array))
  return(list(r_star=a_accuracy, r_hat=mon$zfsRhat))
}

@@

Look at predictions of model
```{r}
# add in a column of noise since gbm requires >1 variables
full_data <- f_generate_lower_var_four(1/3, 0.3, 1, 2000) %>% 
  melt() %>% 
  select(-Var1) %>% 
  rename(chain=Var2) %>% 
  mutate(ran_val=rnorm(8000)) %>% 
  mutate(chain=as.factor(chain))

@@

Generate R* distribution based on 2000 iterations for run where chain has lower variance and another where all four chains have same variance
```{r}
temp <- f_generate_lower_var_four(1/3, 0.3, 1, 2000) 
temp1 <- matrix(rnorm(8000), nrow = 2000)
a_array <- array(dim=c(2000, 4, 2))
a_array[,,1] <- temp
a_array[,,2] <- temp1
unmixed <- r_star_dist(a_array)

temp <- f_generate_lower_var_four(1, 0.3, 1, 2000)
temp1 <- matrix(rnorm(8000), nrow = 1000)
a_array <- array(dim=c(2000, 4, 2))
a_array[,,1] <- temp
a_array[,,2] <- temp1
mixed <- r_star_dist(a_array)

@@

# Show performance as a function of hyperparameters
```{r}
caretGrid <- expand.grid(interaction.depth=c(3), n.trees = 50,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
caretGrid1 <- expand.grid(interaction.depth=c(5), n.trees = 50,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
caretGrid2 <- expand.grid(interaction.depth=c(3), n.trees = 100,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
caretGrid3 <- expand.grid(interaction.depth=c(5), n.trees = 100,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
caretGrid4 <- expand.grid(interaction.depth=c(7), n.trees = 100,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
caretGrid5 <- expand.grid(interaction.depth=c(7), n.trees = 200,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
lgrids <- list(caretGrid, caretGrid1, caretGrid2, caretGrid3, caretGrid4, caretGrid5)
f_replicate_hyper <- function(lgrids){
  temp <- f_generate_lower_var_four(1/3, 0.3, 1, 1000)
  a_array <- array(dim=c(1000, 4, 1))
  a_array[,,1] <- temp
  laccuracy <- vector(length = length(lgrids))
  for(i in seq_along(lgrids))
    laccuracy[i] <- r_star(a_array, caret_default=lgrids[[i]])
  return(laccuracy)
}

nreplicates <- 200
r_star_vals <- matrix(nrow = nreplicates, ncol=length(lgrids))
for(i in 1:nreplicates){
  if(i%%100==0)
    print(i)

  temp <- f_replicate_hyper(lgrids)
  r_star_vals[i, ] <- temp
}

saveRDS(r_star_vals, "../data/ar1_sensitivity.rds")

b_sum <-
  r_star_vals %>% 
  as.data.frame() %>% 
  mutate(iterate=seq(1, nreplicates, 1)) %>%
  melt(id.vars="iterate") %>% 
  mutate(below=if_else(value < 1, 1, 0)) %>% 
  group_by(variable) %>% 
  summarise(below_per=round(mean(below)*100, 1),
            lower=quantile(value, 0.25),
            upper=quantile(value, 0.75),
            middle=median(value)) %>%
  mutate(below_per=paste0(below_per, "%")) %>% 
  mutate(variable=case_when(variable=="V1"~"int.depth=3\nn.trees=50",
                            variable=="V2"~"int.depth=5\nn.trees=50",
                            variable=="V3"~"int.depth=3\nn.trees=100",
                            variable=="V4"~"int.depth=5\nn.trees=100",
                            variable=="V5"~"int.depth=7\nn.trees=100",
                            variable=="V6"~"int.depth=7\nn.trees=200")) %>% 
  arrange(variable) %>% 
  mutate(x_pos=seq(1, 6, 1)) %>% 
  mutate(y_pos=0.95)

g <- r_star_vals %>% 
  as.data.frame() %>% 
  mutate(iterate=seq(1, nreplicates, 1)) %>% 
  melt(id.vars="iterate") %>% 
  mutate(below=if_else(value < 1, 0, 1)) %>% 
  mutate(variable=case_when(variable=="V1"~"int.depth=3\nn.trees=50",
                            variable=="V2"~"int.depth=5\nn.trees=50",
                            variable=="V3"~"int.depth=3\nn.trees=100",
                            variable=="V4"~"int.depth=5\nn.trees=100",
                            variable=="V5"~"int.depth=7\nn.trees=100",
                            variable=="V6"~"int.depth=7\nn.trees=200")) %>% 
  left_join(b_sum, by = "variable") %>%
  ggplot(aes(x=as.factor(variable), y=value, colour=as.factor(below))) +
  geom_jitter() +
  xlab("Hyperparameters") +
  ylab("R*") +
  geom_hline(yintercept = 1, linetype=2) +
  annotate("text", x = b_sum$x_pos, y = b_sum$y_pos, label = b_sum$below_per, size=5) +
  annotate("pointrange", x = 1:6, ymin=b_sum$lower, ymax=b_sum$upper, y = b_sum$middle, colour="black", size=1) +
  coord_flip() +
  scale_color_grey() +
  theme(axis.text = element_text(colour="black", size=12),
        axis.title = element_text(colour="black", size=14),
        legend.position = "none")
ggsave("../output/ar1_sensitivity.pdf", g, width = 12, height = 8)
```

### 2020-05-06 src/s_mvt_normal.Rmd
updated ar1 figures

ga <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=fct_relevel(as.factor(variable), "samples_400", "samples_10000", "samples_10000_ncp"))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("# of draws", labels=c("400, cp", "10000, cp", "10000, ncp")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black"),
        legend.position = c(0.8, 0.8)) +
  ggtitle("A.")

ga2 <- 
  b_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=fct_relevel(as.factor(variable), "samples_400", "samples_10000", "samples_10000_ncp"))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("# of draws", labels=c("400, cp", "10000, cp", "10000, ncp")) +
  xlab(TeX("split-$\\hat{R}$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black"),
        legend.position = c(0.8, 0.8)) +
  ggtitle("B.")

>>>>

ga <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=fct_relevel(as.factor(variable), "samples_400", "samples_10000_cp", "samples_10000_ncp"))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("# of draws", labels=c("400, cp", "10000, cp", "10000, ncp")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black"),
        legend.position = c(0.8, 0.8)) +
  ggtitle("A.")

ga2 <- 
  b_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=fct_relevel(as.factor(variable), "samples_400", "samples_10000_cp", "samples_10000_ncp"))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("# of draws", labels=c("400, cp", "10000, cp", "10000, ncp")) +
  xlab(TeX("split-$\\hat{R}$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black"),
        legend.position = c(0.8, 0.8)) +
  ggtitle("B.")
